WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-12-31 method/sec_1-architectural_decisions.tex
Chap 5: Added discussion paragraph regarding existing systems vs WDIAS
Added feature comparison of the systems

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Architecture Comparison with Existing Systems

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.05\textwidth]{method/misc/architecture_comparison_pros_cons.pdf}
    \caption{Comparison of available features among existing weather data assimilation and integration systems and \acrshort{wdias}. An "X" in the table represents a feature offered by the corresponding tool. An "-" in the table represents that information available are not enough to make an statement, and empty presents a feature is not offered. }
    \label{fi:architecture_comparison}
\end{figure}

\gc{\cref{fi:architecture_comparison} shows a summarized architecture comparison between existing systems that we discussed in the WDIAS. Here, we analyze the systems under a few categories such as data resources of the system, performance, architecture of the system, and other available main features. The fews and msm frameworks store the data through a central data service which can be a bottleneck handling large amounts of data in a critical situation. Other systems are capable of using a resource pool which allows them to grow the performance while adding more resources to the system.  Regarding the performance of the systems, we consider scalability, availability, cloud computing support, and system deployment capabilities. All of the systems are capable of scaling up to some extent by adding resources beforehand or in real time. But the LEAD, DIAS and WDIAS are capable of scaling on demand by adding more resources, and also support auto scaling up and scaling down. The LEAD, MADIS, DIAS and WDIAS able to provide availability, since those were able to run using a resource pool which can run on different locations, and systems are capable of automatically handling partial system failures, hence supporting fault tolerance. When we discuss about the modern cloud computing support, the system should support easy integration with clouds. It is possible to rent virtual servers and deploy the local services in the cloud infrastructure, but some systems may not allow access to them remotely. Even some systems able to deploy in such manner, they may not be capable of automatically resource allocation on demand. Hence, we can not consider that those systems are full cloud infrastructures. Furthermore, we can easily maintain a system if it consists of independent subsystems, and each subsystem is capable of deploying or upgrading independently. Independent service deployment is a more flexible and better way to handle this, rather than copy pasting codes in order to deploy changes.}

\gc{We discuss the architecture of the systems in their pattern, dependencies of the subsystems, extendable with adding more features easily, source code availability, and data preprocessing capabilities specific to the weather domain. While other existing systems are using distributed client server architecture or monolithic distributed architecture, LEAD is using the SOA architecture, but WDIAS has the more advantage of using modern cloud computing technologies with implementing microservices as containerized applications. The architecture implementation of independent subsystems allow users to maintain subsystems independently. Further, WDIAS allow to use own technology stack for each subsystem with using different programming languages. Specially the WDIAS and MSM provide open source framework which gives the capability for users to enhance or modify the system as per the requirement. All of these systems provide data preprocessing capabilities for weather data, and adding new preprocessing capabilities. But WDIAS is capable of providing auto scaling with data preprocessing as well. Workflow engine and model execution support are some other extra features that are helpful with weather forecasting. But the WDIAS focus is about implementing a WDIA system with supporting main features, and it provides an extendable open framework to integrate such features easily.}

### 2020-12-31 summary/sec_1-conclusions.tex
Added feature comparison of the systems

\gc{When compared to other existing weather data integration and assimilation systems, the WDIAS has the advantage of taking full advantage of modern cloud computing technologies to implement a highly scalable and high-available system with low-cost. Since it uses containerized applications to implement the microservices, it allows independent service deployments. Each microservice can scale independently without affecting other microservices, and capable of using suitable technology stack for the task. The \acrshort{fews}, \acrshort{madis} and \acrshort{\acrshort{msm}} have platform dependencies, and some of the deployments are done with copy-pasting source codes. The \acrshort{fews} and \acrshort{msm} provide centralized data storage mechanism which can become a bottleneck while processing a huge set of data in critical situations. The \acrshort{madis} and \acrshort{dias} also support data storage array to store data. The WDIAS and \acrshort{lead} can support a pool of resources based on the requirement.
Similar to other systems, WDIAS provides the data preprocessing capabilities, and users can integrate new data preprocessing capabilities by implementing as independent containerized microservice applications. Even though \acrshort{fews}, \acrshort{lead} and \acrshort{msm} provide workflow engine support and model execution support, these can be achieved using an external workflow management system by fulfilling the data requirements via WDIAS system. Further, WDIAS is an extendable open framework such that similar capabilities can be integrated as a new extension module system. Compared to other existing systems, the \acrshort{lead} is more scalable which is implemented using \acrshort{soa} architecture as a result of contributions of lots of research from multiple universities. But with the help of modern container orchestration frameworks such as Kubernetes and cloud computing technologies, those are able to provide high scalability and high availability as inherent capabilities. And those are mature enough to automatically provide fault-tolerance \cite{Scolati2019ADevices}. By implementing the deployment units as containerized applications based on the modern architecture patterns allow WDIAS to implement a highly scalable and high available system without heavy effort on those features.}

>>>>

\gc{When compared to other existing weather data integration and assimilation systems, the WDIAS has the advantage of taking full advantage of modern cloud computing technologies to implement a highly scalable and high-available system with low-cost. Since it uses containerized applications to implement the microservices, it allows independent service deployments. Each microservice can scale independently without affecting other microservices, and capable of using suitable technology stack for the task. The \acrshort{fews}, \acrshort{madis} and \acrshort{msm} have platform dependencies, and some of the deployments are done with copy-pasting source codes. The \acrshort{fews} and \acrshort{msm} provide centralized data storage mechanism which can become a bottleneck while processing a huge set of data in critical situations. The \acrshort{madis} and \acrshort{dias} also support data storage array to store data. The WDIAS and \acrshort{lead} can support a pool of resources based on the requirement.
Similar to other systems, WDIAS provides the data preprocessing capabilities, and users can integrate new data preprocessing capabilities by implementing as independent containerized microservice applications. Even though \acrshort{fews}, \acrshort{lead} and \acrshort{msm} provide workflow engine support and model execution support, these can be achieved using an external workflow management system by fulfilling the data requirements via WDIAS system. Further, WDIAS is an extendable open framework such that similar capabilities can be integrated as a new extension module system. Compared to other existing systems, the \acrshort{lead} is more scalable which is implemented using \acrshort{soa} architecture as a result of contributions of lots of research from multiple universities. But with the help of modern container orchestration frameworks such as Kubernetes and cloud computing technologies, those are able to provide high scalability and high availability as inherent capabilities. And those are mature enough to automatically provide fault-tolerance \cite{Scolati2019ADevices}. By implementing the deployment units as containerized applications based on the modern architecture patterns allow WDIAS to implement a highly scalable and high available system without heavy effort on those features.}
